\TitlePt

### 2016-03-19 introduction.tex
Tweaks to last paragraphs of introduction

Deriving geophysical Earth models from observed gravity data is an ill-posed
inverse problem.
Designing a method for solving these inverse problems presents many challenges.
The first challenge is to establish a functional mapping between the model
parameters and the data.
This is known as the forward problem and it must be solved in a stable and
accurate way for the inversion to succeed.
The second challenge is to choose and implement an optimization algorithm to
estimate the model parameters that best fit the observed data.
There are several well established optimization methods to choose from the
literature, for example, gradient-descent methods like the Gauss-Newton method
and Steepest Descent or stochastic  methods like the Genetic Algorithm.
The optimization method is independent of the forward problem.
Finally, there is the challenge of stabilizing the inverse problem.
This is often done through some form of regularization.
Each regularizing function favors different attributes, such as smoothness or
compactness.
Choosing an appropriate regularizing function is an indirect way to include
prior geological or geophysical information.

When developing a new inversion methodology, one must implement in a software
application all three components of an inversion method (forward problem,
optimization, and regularization).
Luckily, the components can usually be uncoupled.
The forward problem does not depend on the optimization and regularization.
Likewise, the optimization algorithm requires only a knowledge of a function to
optimize (and possibly its derivatives), no matter what is the forward problem
or regularizing function.
Changing the regularizing function used in principle does not require changes
to the forward problem or the optimization method.
Thus, the ideal implementation would be to have independent and reusable
forward modeling, optimization, and regularization routines.

Here, we develop two software projects and apply their reusable components to
develop a 3D gravity inversion method in spherical coordinates.
Chapter~\ref{chap:tesseroids} describes the open-source software
\textit{Tesseroids}.
This C language program calculates the gravitational potential and its first
and second derivatives of a tesseroid (or spherical prism).
The software also improves upon existing algorithms for the forward modeling
calculations.
Chapter~\ref{chap:fatiando} describes the Python language library
\textit{Fatiando a Terra}.
The library contains a collection of functions and classes for forward
modeling, data and model visualization, data processing, and inversion.
The optimization and regularization components are uncoupled from specific
forward problems.
Thus, they can be reused and combined to implement new inversion methods.
\textit{Fatiando a Terra} also implements the tesseroid forward modeling
algorithm described in Chapter~\ref{chap:tesseroids}.
Finally, in Chapter~\ref{chap:moho} we build upon the foundation of
Chapters~\ref{chap:tesseroids} and \ref{chap:fatiando} to develop a novel
gravity inversion method.
The method estimates the depth of the crust-mantle interface (the Moho) in a
spherical approximation from observed gravity data.
The software implementation of the inversion combines and extends the
optimization, regularization, and tesseroid forward modeling available in
\textit{Fatiando a Terra}.
We apply our method to estimate the depth of the Moho for the South American
continent.
The estimated Moho depths agree with previous models and known large-scale
tectonic features.

>>>>

Deriving geophysical Earth models from observed gravity data is an ill-posed
inverse problem.
Designing a method for solving these inverse problems presents many challenges.
The first challenge is to establish a functional mapping between the model
parameters and the data.
This is known as the forward problem and it must be solved in a stable and
accurate way for the inversion to succeed.
The second challenge is to choose and implement an optimization algorithm to
estimate the model parameters that best fit the observed data.
There are several well established optimization methods to choose from the
literature, for example, gradient-descent methods like the Gauss-Newton method
and Steepest Descent or stochastic  methods like the Genetic Algorithm.
Finally, there is the challenge of stabilizing the ill-posed inverse problem,
usually through regularization.
Different regularizing functions favor different model attributes, such as
smoothness or compactness.
Choosing an appropriate regularizing function is an indirect way to include
prior geological or geophysical information in the inverse problem.

When developing a new inversion methodology, one must implement in a software
application all three components of an inversion method (the forward problem,
optimization, and regularization).
Luckily, the components can usually be uncoupled.
For example, the implementation of the forward problem does not depend on the
choice of optimization method or regularization.
Likewise, the software implementation of optimization requires only a knowledge
of a function to optimize (and possibly its derivatives), no matter what is the
forward problem or regularizing function.
Furthermore, changing the regularizing function used, in principle, does not
require changes to the implementations of the forward problem and the
optimization method.
Thus, the ideal software design is to have independent and reusable routines
for forward modeling, optimization, and regularization.
These three components can be combined in different ways to produce
new inversion software.

Here, we develop two software projects and apply their reusable components to
develop a 3D gravity inversion method in spherical coordinates.
Chapter~\ref{chap:tesseroids} describes the open-source software
\textit{Tesseroids}.
This C language program calculates the gravitational potential and its first
and second derivatives of a tesseroid (or spherical prism).
The software also improves upon existing algorithms for the forward modeling
calculations.
Chapter~\ref{chap:fatiando} describes the Python language library
\textit{Fatiando a Terra}.
The library contains a collection of functions and classes for inverse
problems, forward modeling, data and model visualization, and data processing.
The inverse problems tools implement optimization and regularization classes
that are uncoupled from specific forward problems.
These tools can be reused and combined in different ways to implement new
inversion methods.
\textit{Fatiando a Terra} also implements the tesseroid forward modeling
algorithm described in Chapter~\ref{chap:tesseroids}.
Finally, in Chapter~\ref{chap:moho} we build upon the foundation of
Chapters~\ref{chap:tesseroids} and \ref{chap:fatiando} to develop a novel
gravity inversion method.
The method estimates the depth of the crust-mantle interface (the Moho) from
observed gravity data using a spherical Earth approximation.
The software implementation of the inversion combines and extends the
optimization, regularization, and forward modeling available in
\textit{Fatiando a Terra}.
We apply our method to estimate the depth of the Moho for the South American
continent.
